











\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 
 
\name{Jeremy A. Cantu\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Current Address} \\   11011 Domain Drive \\   Austin, TX
         78758   \\ (956)286-8386}
\address{{\bf Contact Information} \\ jeremycantu.com \\ github.com/jac21 \\ mail@jeremycantu.com}
 
                                             
\begin{resume}
                                               
 
\section{Objective and Summary}
   Jeremy originally hails from the border city of Laredo Texas, thereafter attending Texas A\&M University in College Station, where he earned his degree in Computer Science with a concentration in Systems Engineering. He has an avid interest in Microsoft .NET technologies, as well as full-stack web development. His current goals involve utilizing his skill-set within the aforementioned fields to both bring value to his role, and further his overall repertoire of technologies and concepts.
 
\section{Work Experience}

Software Development Engineer \\
Charles Schwab \\
April 2019 - Present
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Software Development Engineer, specializing in distributed, scalable, and performant back-end financial technology applications and services, utilizing .NET Core C\#, WebAPI, and NoSQL database Aerospike in an Agile and Cloud based environment. 
\newline
    \item In addition to the above, other responsibilities include application metric analysis and business intelligence augmentation via the utilization of Splunk machine data indexing and visualization tools, as well as its associated query language.
 \end{itemize}

Software Developer \\
Advanced Solutions International \\
January 2017 - Present
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Full-stack, .NET-focused software developer, specializing in C\#, JavaScript, HTML5, and CSS3 based web-development, including back-end (Entity Framework, T-SQL) and RESTful API (WebAPI) middle-ware technologies. The aforementioned takes place in an Agile, Scrum-based environment.
\newline
    \item Responsibilities also include quarterly product penetration-testing involving vulnerability scanning tools such as Arachni and Burp Suite, as well as database injection tools such as SQLMap.
 \end{itemize}

 Software Developer \\
Dell \\
April 2016 - January 2017
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Software Developer Engineer in Test, as part of the Dell Consumer Services "Responsive Platform" team. Responsible for automated test framework and suite creation for the whole of the application, utilizing C\#, Selenium WebDriver, and SpecFlow, as well as monitoring and analysis using Splunk and Adobe Analytics.
 \end{itemize}

\section{Current Skillset} 
 
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Languages: Proficient in .NET C\# (7.0) and JavaScript (ES5, ES6)
\\
   \item Front-end Web Development: Proficiency with HTML5, CSS3, NPM dependency management, experience with the Angular framework and React library
\\
    \item Back-end Web Development: Proficiency in .NET stacks involving ASP.NET WebAPI, Entity Framework and T-SQL, NoSQL data-store Aerospike, experience with JavaScript stacks involving Node.JS
 \end{itemize}
 
\section{Education} 
 \noindent Texas A\&M University, College Station, Texas - May 2015 \\
B.S. Computer Science, Systems Engineering Track \\
Relevant Courses: Design and Analysis of Algorithms, Distributed Objects Programming, Networks and Distributed Programming

\end{resume}
\end{document}











